% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{NATHAN T. HUI}
% \address used twice to have two lines of address
\address{13336 Tobiasson Rd, Poway, CA 92064}
\address{nthui@ucsd.edu, (408) 838-5393}


\begin{resume}

\section{OBJECTIVE}
	Engineering student looking to explore embedded systems and robotics, particularly embedded control systems, embedded sensor networks, and low-level data aggregation from the perspective of developing technologies to enable scientific research.
	%Looking for an engineering position in researching, designing, and building autonomous vehicles in a challenging and dynamic team environment.
	%Looking for a position working with groups in the outdoors with a focus in safety and/or search and rescue.

\section{EDUCATION}
	{\sl Masters of Science,} Electrical Engineering (Intelligent Systems, Robotics, and Controls)\\
	UC San Diego, San Diego, CA, March 30 2017 to September 7 2019\\
	GPA: 3.005 / 4.000
	Major GPA: 3.141

	{\sl Bachelor of Science,} Electrical Engineering \\
	UC San Diego, San Diego, CA, September 24 2012 to March 25 2017\\
	GPA: 3.092 / 4.000
	Major GPA: 3.106

\section{PROJECT AND RESEARCH EXPERIENCE}
	{\sl Triton Robosub - Mentor} \hfill January 7 2019 - current
	\begin{itemize}
		\item 
	\end{itemize}

	{\sl UCSD E4E / CISA3 - Project Lead} \hfill January 2 2014 - current
	\begin{itemize}
		\item Leading the development, testing, and deployment of C/C++ and Python embedded software and computing hardware for aerial ecological radio transmitter tracking surveys, using software-defined radios to detect transmissions and embedded Linux single-board computers for online processing.
		\item Leading the development, testing of 3D printed mechanical subsystems in SolidWorks for mounting scientific payloads to multirotor aircraft.
		\item Developed and deployed embedded C software onto an ATMega microprocessor for controlling a sensor payload and aggregating data from low-level sensors over serial communications.
		\item Designed and built a single-board computer supporting an ATMega microprocessor for integrating sensor data and user interface hardware.
		\item Explored technology to dynamically generate and optimize drone flight paths for aerial survey using real-time feedback from cameras and other drone sensors, including terrain following/mapping and source seeking techniques.
		\item Developed integrated 3-D visual mapping tools using stereo cameras to enable researchers to make high-quality 3-D models of areas in near real-time under an Undergraduate Research Fellowship from the Center of Integrated Access Networks (CIAN) in 2015.
		\item Developed a stabilization controller in C on an embedded microcontroller for an actively stabilized DSLR mount for a persistent aerial survey platform, aimed at providing researchers with a wide-angle view coupled with pan-capable zoom imagery.
		\item Mentoring and managing students working on various research projects.
		\item Conducted daytime and nighttime test flights and scientific survey flights of a multirotor-based wildlife tracking system using radio transmitters.
		\item Integrated radio tracking sensor payloads into multiple multirotor systems using design and requirements analysis to enable robust long-endurance survey flights in austere environments.
		\item Analyzed post-crash telemetry in deployed and testing enviornments to determine and mitigate causes of crashes to facilitate system robustness.
		\item Conducted scientific survey flights of multirotor-based aerial photography systems to capture imagery of Maya ruins in Guatemala to facilitate developing 3D models of ancient Maya cities.
		\item Provided autopilot monitoring and ground support for fixed-wing drone-based mapping flights to capture imagery of Guatemalan forests to facilitate developing topographic maps to help guide archaeologists.
		\item Instructed student pilots in practical and theoretical aspects of flying SUAS in preparation for operating drones on scientific deployments.
		\item Operated the autopilot and ground station for multirotor-based thermal imaging to detect birds in nests for ecological surveys.
		\item Primary Investigator: Ryan Kastner, (858) 534-3534, kastner@ucsd.edu; Curt Schurgers, (858) 246-1442, cschurgers@ucsd.edu
	\end{itemize}

	{\sl UCSD SIO Jaffe Lab - Graduate Researcher} \hfill March 28 2018 - August 30 2018
	\begin{itemize}
		\item Utilized Python to develop a distributed control system for a hemispherical multicamera array run by a cluster of Raspberry Pi Zeros, and created a workflow to synchronize and stitch immersive video from the camera array.
		\item Improved the design of the structural support for the multi-camera array in Solidworks to improve stability and rigidness.
		\item Supported a deployment of a plankton camera on a Conductivity, Temperature, and Depth sensor rig on the R/V Gordon Sproul.
		\item Primary Supervisor: Paul Roberts (858) 534-8151, plroberts@ucsd.edu, Jules Jaffe (858) 534-6101
	\end{itemize}

	{\sl UCSD Veridrone - Graduate Researcher} \hfill March 30 2017 - June 15 2018
	\begin{itemize}
		\item Mentored an undergraduate research project examining using machine learning to predict multirotor failures by examining real-time telemetry.
		\item Performed state space exploration of slow discrete time implementation of source seeking algorithms.
		\item Primary Investigators: Ryan Kastner, (858) 534-3534, kastner@ucsd.edu; Sorin Lerner, (858) 534-8883, lerner@ucsd.edu; Miroslav Krstic, (858) 534-5556, mkrstic@ucsd.edu
	\end{itemize}

	{\sl UCSD AUVSI - System Lead} \hfill September 24 2012 - June 13 2014
	\begin{itemize}
		\item Led development of an actively stabilized composite DSLR gimbal, composite payload computer enclosure, composite payload launcher, composite battery carrier, and autopilot enclosure with minimized system volume and weight.
		\item Developed embedded software on a 32-bit ARM microcontroller to aggregate telemetry from an autopilot, camera gimbal, and imaging system and forward the summarized data to an image processing pipeline.
		\item Developed and validated embedded software on an 8-bit Atmel microcontroller in C to analyze and generate control signals for use in an RC failsafe device.
		\item Developed a DSLR gimbal from scratch with SolidWorks and various machine tools for isolating the imaging system from airframe during flight.
		\item Provided autopilot monitoring and ground support for test and competition flights.
	\end{itemize}

	{\sl UCSD Human Powered Submarine - Mechanical Engineer} \hfill September 24 2012 - June 14 2013
	\begin{itemize}
		\item Developed an integrated a dual-input synchronized power train from scratch for a human powered submarine with SolidWorks and various machine tools.
		\item Managed and organized CAD system for entire project to enable multiple designers to collaborate on the same SolidWorks assembly.
	\end{itemize}

	% {\sl FIRST Robotics Competition - Team Captain} \hfill Fall 2010 - Spring 2012
	% \begin{itemize}
	% 	\item Mentor, Team Captain, System Lead for CHS Robotics (FRC 2473).
	% 	\item Designed and built a pneumatic minibot deployment arm, ball pickup, chassis, and control system carrier leveraging CAD and systems design techniques.
	% 	\item Developed limited computer vision algorithms for target recognition and ranging in C++ and Java
	% \end{itemize}

\section{WORK EXPERIENCE}
	{\sl UC San Diego COSMOS - Cluster Assistant} \hfill March 30 2017 - Aug 30 2018
	\begin{itemize}
		\item Developed and implemented lesson plans to teach middle school students about robotics.
		\item Managed daily lab sessions where middle school students designed, assembled, and tested robots to complete various challenges.
		\item Supervisor: Curt Schurgers, (858) 246-1442, cschurgers@ucsd.edu; Michael Yip, (858) 822-4778, yip@ece.ucsd.edu
	\end{itemize}

	{\sl UCSD Outback Adventures - Lead Guide} \hfill January 2 2013 - January 15 2019
	\begin{itemize}
		\item Mentoring new staff in developing technical and interpersonal skills.
		\item Leading trips of students, staff, faculty, and community members to locations throughout the Southwestern United States and Western Mexico, providing instruction and leadership in outdoor activities including hiking, climbing, camping, caving, and kayaking.
		\item Presented various technical and leadership workshops at the Western Region Outdoor Leadership Conference, including \textit{Emergency Backcountry Communications}, \textit{Photography on Vertical Terrain}, and \textit{Facilitating Staff Development on Trips}.
		\item Directed race planning and execution for UCSD Outback Adventures 2015 and 2014 Moon God 5K run, resulting in an improvement in race participation and net gains.
		\item Supervisor: Simon Teale, (858) 534-3534, steale@ucsd.edu
	\end{itemize}
	{\sl UCSD Outback Adventures - Rental Shop Student Manager} \hfill January 2 2013 - January 15 2019
	\begin{itemize}
		\item Managing and repairing outdoor equipment, including climbing gear, kayak trailers, first aid kits, skis, and snowboards to improve equipment readiness for trips and prolong equipment lifetimes.
		\item Rented outdoor recreation equipment to students, staff, faculty, and community members, and provided customer support to assist clients in planning and preparing for their outdoor adventures.
		\item Directed and implemented the transitioning of the Rental Shop to new Point of Sale and Rental Management software.
		\item Directed moving of all outdoor recreational equipment and retail inventory to a new location with fast deadline to operational status.
		\item Provided business operations support to other Outback Adventures programs in handling client payments, equipment usage and storage, and other general business administrative tasks.
		\item Mentoring new staff in developing technical and interpersonal skills.
		\item Supervisor: Tom Rottler, (858) 534-9098, trottler@ucsd.edu
	\end{itemize}

	{\sl Biosero LLC - Engineering Associate} \hfill June 30 2013 - September 20 2013
	\begin{itemize}
		\item Optimized tube cap removal device performance and systems integration, formalizing system specifications and integration with company automation products.
		\item Designed low-cost automated plate handling system using SolidWorks for coupling two automated liquid handling enclosures.
		\item Developed extensible code structure for software integration with touch screens, permitting intuitive user interface with automated liquid handling enclosures.
		\item Leveraged statistical computation capabilities of Microsoft Excel to analyze accuracy and precision of automated syringe pumps.
		\item Supervisor: Alice Tanibata, (858) 525-1645, alicetanibata@biosero.com
	\end{itemize}

\section{PILOTING EXPERIENCE}
	{\sl FAA Part 107 Small Unmanned Aerial Systems} \hfill Issued November 2016\\
	36 PIC hours, 10 FI hours\\
	\begin{itemize}
		\item Tarot Ironman 650 - 20 Hours
		\item 3DR Solo - 15 Hours
		\item FoxTech Hover 1 - 10 Hours
		\item DJI Spreading Wings S800 - 3 hours
		\item 3DR Iris - 1 Hour
	\end{itemize}

\section{RELEVANT COURSEWORK}
	{\sl M.S. Electrical Engineering, UCSD}
	\begin{itemize}
		\item ECE 299 - Independent Research
		\item ECE 285 - Intelligent Vehicles / Assisted Systems
		\item ECE 276A - Sensing and Estimation in Robotics
		\item ECE 275A - Statistical Parameter Estimation
		\item ECE 272A - Stocastic Processes and Dynamic Systems
		\item ECE 271A - Statistical Learning
		\item ECE 269 - Linear Algebra and Application
		\item ECE 250 - Random Processes
		\item ECE 180 - Software Systems
		\item ECE 180 - Smart Power Systems
		\item ECE 180 - GPU Programming
		\item ECE 143 - Programming for Data Analysis
		\item ECE 120 - Solar System Physics
		\item ECE 115 - Fast Prototyping
		\item CENG 114 - Probability and Statistical Methods for Engineers
		\item CSE 237B - Software for Embedded Systems
		\item CSE 237C - High Level Synthsis
		\item ENVR 140 - Wilderness and Human Values
		\item MAE 140 - Linear Circuits
	\end{itemize}

	{\sl B.S. Electrical Engineering, UCSD}
	\begin{itemize}
		\item ECE 174 - Intro to Linear and Nonlinear Optimizations
		\item ECE 172A - Introduction to Intelligent Systems
		\item ECE 111 - Digital Design Project
		\item ECE 109 - Engineering Probability and Statistics
		\item ECE 107 - Electromagnetism
		\item ECE 103 - Fundamentals of Devices and Materials
		\item ECE 102 - Introduction to Active Circuit Design
		\item ECE 101 - Linear Systems Fundamentals
		\item ECE 100 - Linear Electronic Systems
		\item ECE 65 - Components And Circuits Lab
		\item ECE 45 - Circuits and Systems
		\item ECE 35 - Introduction to Analog Design
		\item ECE 30 - Introduction to Computer Engineering
		\item ECE 25 - Introduction to Digital Design
		\item ECE 15 - Engineering Computation
		\item CSE 237A - Introduction to Embedded Computing
		\item CSE 145 - Embedded System Design Project
		\item CSE 141 - Introduction to Computer Architecture
		\item CSE 140 - Component and Design Technologies / Digital Systems
		\item CSE 140L - Digital Systems Laboratory
		\item CSE 120 - Principles of Computer Operating Systems
		\item CSE 110 - Software Engineering
		\item CSE 101 - Design and Analysis of Algorithms
		\item CSE 100 - Advanced Data Structures
		\item CSE 30 - Computer Organization and Systems Programming
		\item CSE 21 - Math / Algorithms and Systems Analysis
		\item CSE 20 - Introduction to Discrete Mathematics
		\item CSE 15L - Software Tools and Techniques Lab
		\item CSE 12 - Basic Data Structures and Object Oriented Design
		\item CSE 11 - Introduction to Computer Science and Object Oriented: Java
		\item MATH 31BH - Honors Multivariable Calculus
		\item MATH 31AH - Honors Linear Algebra
		\item MATH 20E - Vector Calculus
		\item MATH 20D - Introduction to Differential Equations
		\item PHYS 2D - Physics: Relativity and Quantum Physics
		\item PHYS 2C - Physics: Fluids, Waves, Thermodynamics, Optics
		\item PHYS 2B - Physics: Electricity and Magnetism
		\item PHYS 2A - Physics: Mechanics
		\item BILD 3 - Organismic And Evolutionary Biology
		\item PSYC 7 - General Psychology: Developmental Fundamentals
		\item ECON 1 - Principles of Microeconomics
		\item HUM 5 - Modern Culture (1848 - Present)
		\item HUM 4 - Enlightenment, Romanticism, Revolution (1660 - 1848)
		\item HUM 3 - Renaissance, Reform, and Early Europe
		\item HUM 2 - Rome, Christianity and the Middle Ages
		\item HUM 1 - Foundations of Western Civilization: Israel and Greece
		\item ETHN 1A - Introduction to Populations Histories of the US
		\item TDDE 1 - Introduction to Design for the Theatre
		\item LTEN 23 - Literature: British Isles: 1832 - Present
		\item SIO 30 - The Oceans
		\item CHIN 20AD - Second Year Chinese - Dialect Speaker
	\end{itemize}

\section{EXPEDITION EXPERIENCE}
	{\sl UCSD Jaffe Lab} \hfill Summer 2018
	\begin{itemize}
		\item Research Cruise, California Coast, 1 day, August 2018, Technical Crew
	\end{itemize}

	{\sl UCSD Engineers For Exploration} \hfill Spring 2015 - current
	\begin{itemize}
		\item Blueprint Earth, Mojave Desert, California. 3 days, November 2016, Sr. Engineer
		\item Radio Collar Tracker, Little Cayman, Cayman Islands. 10 days, May 2016, Operations Lead
		\item Radio Collar Tracker, Pedernales, Dominican Republic. 10 days, September 2015, Operations Lead
		\item Radio Collar Tracker, Pedernales, Dominican Republic. 14 days, July 2015, Operations Lead
		\item Maya Archeology, Peten, Guatemala. 7 days, May 2015, Technical Staff
	\end{itemize}

	{\sl UCSD Outback Adventures} \hfill Winter 2013 - Winter 2019
	\begin{itemize}
		\item Rock Climbing, Mission Gorge, California, 1 day, February 2019, Lead Guide
		\item Kayaking, Black Canyon, Arizona, 3 days, November 2018, Lead Guide (Mock Lead Supervisor)
		\item Caving, Anza Borrego, California, 2 days, November 2018, Lead Guide
		\item Backpacking, San Gorgonio, California, 2 days, October 2018, Lead Guide
		\item Canoing, Black Canyon, Arizona, 4 days, September 2018, Lead Guide (Mock Lead Supervisor)
		\item Kayaking, Coronado Bay, California, 1 day, August 2018, Lead Guide
		\item Kayaking, Mission Bay, California, 1 day, June 2018, Lead Guide
		\item Kayaking, La Jolla Shores, California, 1 day, May 2018, Lead Guide
		\item Snorkeling, La Jolla Cove, California, 1 day, May 2018, Lead Guide
		\item Snorkeling, La Jolla Cove, California, 1 day, April 2018, Lead Guide
		\item Kayaking, La Jolla Shores, California, 1 day, April 2018, Lead Guide
		\item Service Adventure, Catalina Island, California, 6 days, March 2018, Lead Guide
		\item Caving, Anza Borrego, California, 2 days, March 2018, Lead Guide
		\item Rock Climbing, Mission Gorge, 1 day, January 2018, Lead Guide
		\item Rock Climbing, Joshua Tree, 2 days, January 2018, Member
		\item Canoing, Black Canyon, Arizona, 4 days, November 2017, Lead Guide
		\item Caving, Anza Borrego, California, 2 days, October 2017, Lead Guide
		\item Canoing, Black Canyon, Arizona, 6 days, September 2017, Lead Guide
		\item Camping, Mt. Laguna, California, 2 days, August 2017, Lead Guide
		\item Kayaking, Mission Bay, California, 1 day, July 2017, Lead Guide
		\item Kayaking, Baja California, Mexico, 7 days, June 2017, Member
		\item Caving, Anza Borrego, California, 2 days, May 2017, Lead Guide
		\item Hiking, Mt. Laguna, California, 1 day, May 2017, Lead Guide
		\item Caving, Anza Borrego, California, 2 days, May 2017, Lead Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, April 2017, Lead Guide
		\item Kayaking, Coronado Bay, California, 1 day, April 2017, Lead Guide
		\item Kayaking, Mission Bay, California, 1 day, April 2017, Lead Guide
		\item Kayaking, Black Canyon, Arizona, 6 days, March 2017, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, February 2017, Secondary Guide
		\item Rock Climbing, Joshua Tree, California, 1 day, January 2017, Secondary Guide
		\item Rock Climbing, Joshua Tree, California, 5 days, January 2017, Member
		\item Rock Climbing, Mission Gorge, California, 1 day, November 2016, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, October 2016, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, September 2016, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, August 2016, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, August 2016, Secondary Guide
		\item Snorkeling, La Jolla Cove, California, 1 day, August 2016, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, July 2016, Secondary Guide
		\item Camping, Mt. Laguna, California, 2 days, July 2016, Secondary Guide
		\item Mountaineering, Sierra Nevada, California, 9 days, June 2016, Member
		\item Rock Climbing, Mission Gorge, California, 1 day, May 2016, Secondary Guide
		\item Kayaking, Coronado Bay, California, 1 day, April 2016, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, February 2016, Secondary Guide
		\item Caving, Anza Borrego, California, 1 day, February 2016, Secondary Guide
		\item Caving, Anza Borrego, California, 2 days, January 2016, Secondary Guide
		\item Kayaking, Black Canyon, Arizona, 4 days, November 2015, Secondary Guide
		\item Backpacking, Joshua Tree, 3 days, November 2015, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, October 2015, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, October 2015, Secondary Guide
		\item Canoing, Black Canyon, Arizona, 6 days, September 2015, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, May 2015, Secondary Guide
		\item Caving, Anza Borrego, California, 2 days, April 2015, Secondary Guide
		\item Service Adventure, Catalina Island, California, 6 days, March 2015, Secondary Guide
		\item Backpacking, Joshua Tree, California, 3 days, February 2015, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, February 2015, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, December 2014, Secondary Guide
		\item Kayaking, Black Canyon, Arizona, 4 days, November 2014, Secondary Guide
		\item Hiking, Cowles Mountain, California, 1 day, November 2014, Secondary Guide
		\item Hiking, Cowles Mountain, California, 1 day, November 2014, Secondary Guide
		\item Caving, Anza Borrego, California, 2 days, November 2014, Secondary Guide
		\item Snorkeling, La Jolla Cove, California, 1 day, October 2014, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, October 2014, Secondary Guide
		\item Camping, Mt. Laguna, California, 2 days, August 2014, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, May 2014, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, May 2014, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, May 2014, Secondary Guide
		\item Kayaking, Mission Bay, California, 1 day, April 2014, Secondary Guide
		\item Rock Climbing, Mission Gorge, California, 1 day, February 2014, Secondary Guide
		\item Rock Climbing, Joshua Tree, California, 3 days, January 2014, Member
		\item Kayaking, Mission Bay, California, 1 day, May 2013, Assistant Guide
		\item Backpacking, Joshua Tree, California, 2 days, January 2013, Member
		\item Kayaking, Black Canyon, Arizona, 4 days, November 2012, Member
	\end{itemize}

	{\sl Personal}
	\begin{itemize}
		\item Off-roading, Diablo Drop-off, Anza Borrego Desert State Park, California, 1 day, March 2019
		\item Climbing, Yosemite, 2 days, October 2018
		\item Caving, Anza Borrego, California, 1 day, August 2018
		\item Climbing, Joshua Tree National Park, 2 days, February 2017
		\item Climbing, New Jack City, California, 2 days, January 2017
		\item Climbing, Red Rocks National Conservation Area, Nevada, 3 days, November 2017
		\item Climbing, Alabama Hills, California, 3 days, November 2016
		\item Backpacking, Joshua Tree National Park, California, 2 days, February 2016
		\item Caving, Anza Borrego, California, 3 days, December 2015
	\end{itemize}

	{\sl Top Climbing Pitches}
	\begin{itemize}
		\item North Arete (5.8, Alpine, 4 pitches), Mammoth Lakes Area, California, September 2018
		\item Change of Scene (5.10a, 1 pitch), New Jack City, California, January 2018
		\item Fine Day (5.10a, 1 pitch), New Jack City, California, January 2018
		\item Moon Where the Wind Blows (5.9, 1 pitch), Red Rocks National Preserve, Nevada, November 2017
		\item Manifest Destiny (5.9+, 1 pitch), Red Rocks National Preserve, Nevada, November 2017
		\item Ming Dynasty (5.9+, 1 pitch), Red Rocks National Preserve, Nevada, November 2017
		\item This is Sparta (5.9, 1 pitch), Red Rocks National Preserve, Nevada, November 2017
		\item Leonids (5.9, 3 pitches), El Cajon Mountain, California, February 2017
	\end{itemize}

\section{VOLUNTEER EXPERIENCE}
	{\sl UCSD Robosub - Mentor} \hfill November 1 2018 - current
		\begin{itemize}
			\item Mentored the UCSD Robosub team in improving their AUV by instructing students in soldering, diagnosing electrical systems issues, mechanical design, and systems design.
			\item Mentored the team in applying and developing foundational leadership and teamwork skills.
		\end{itemize}
	{\sl Catalina Environmental Leadership Program}
		\begin{itemize}
			\item 12 hours, March 2018, Catalina Island, Environmental service and trail work
			\item 12 hours, March 2015, Catalina Island, Environmental service and trail work
		\end{itemize}

	{\sl Pacific Crest Trail Association}
		\begin{itemize}
			\item 16 hours, March 2016, Santa Clarita, Trail work
		\end{itemize}

	{\sl Allied Climbers, San Diego}
		\begin{itemize}
			\item 8 hours, October 2016, Mission Trails Regional Park, Trail work
		\end{itemize}

\section{ADDITIONAL SKILLS}
	{\sl Outdoor Leadership}\\
		Wilderness First Responder, Conflict Resolution, Experiential Learning, Group Management

	{\sl Outdoor Technical Skills}\\
		Sea Kayaking (including surf launch/recovery, Eskimo roll, kayak repair, towing), Canoing, Rock Climbing (including top rope belay, anchor placement and setup, counter-balance ascent, single rope technique, lead climbing, trad climbing, gear placement, aid climbing, multipitch climbing), Land Navigation, Class B CDL

	{\sl Unmanned Aerial Vehicles}\\
		Part 107 Small Unmanned Aerial Systems Pilot

\section{PORTFOLIO}
	{\sl Linkedin} - https://www.linkedin.com/in/ntlhui

	{\sl Github} - https://github.com/ntlhui
\end{resume}
\end{document}

